Plant-pollintor networks worldwide are composed by the same specific building

### 2021-06-15 Draft/Draft.Rmd
edits on heatmap

@@

h_pol <- Heatmap(long_m, name = "Mean\npercentile", row_split=r_split,cluster_row_slices = FALSE, 
        column_title = "Pollinator functional\ Groups",row_names_gp = gpar(fontsize = 12),col = col_fun)

@@

long_plants_1$Functional_groups[long_plants_1$Functional_groups==1] <- "Cluster 1" 
long_plants_1$Functional_groups[long_plants_1$Functional_groups==2] <- "Cluster 2" 
long_plants_1$Functional_groups[long_plants_1$Functional_groups==3] <- "Cluster 3" 
long_plants_1$Functional_groups[long_plants_1$Functional_groups==4] <- "Cluster 4" 
long_plants_1$Functional_groups[long_plants_1$Functional_groups==5] <- "Cluster 5"

long_plants_1$Functional_groups <- factor(long_plants_1$Functional_groups, levels=c("Cluster 1",
"Cluster 2" ,"Cluster 3","Cluster 4" ,"Cluster 5" ))

@@

h_plan <- Heatmap(long_plants_m, name = "Mean\npercentile", row_split=r_split_plants,cluster_row_slices = FALSE, 
        column_title = "Plant functional\ Groups",row_names_gp = gpar(fontsize = 12),col = col_fun)

library(patchwork)
h_pol+h_plan

@@

ggplot(ggd1,offset_labels=-0.05) + theme(panel.grid.major = element_blank(),
 axis.text = element_blank(),axis.title = element_blank()) +
  ggtitle("Plant functional groups")+
  theme(plot.title = element_text(hjust = 0.5, vjust = -2,size = 20,face="bold"))+
  annotate("text", x=140, y=1.65, label= "Perennials self-incompatible large flowers ", size=2.5)+
  annotate("text", x=380, y=2.15, label= "Tall plants small unisexual flowers", size=2.5) +
  annotate("text", x=600, y=3.85, label= "Short-lived selfers", size=2.5) +
  annotate("text", x=1400, y=2.05, label= "Short-lived non-selfers \n long zygomorphic flowers", size=2.5) +annotate("text", x=950, y=2.05, label= "Small non-selfers perennials", size=2.5)

>>>>

cite complexheatmap https://doi.org/10.1093/bioinformatics/btw313

@@

h_pol <- Heatmap(long_m, name = "Mean\npercentile", row_split=r_split,cluster_row_slices = FALSE, 
                 column_title = "Pollinator functional groups",row_names_gp = gpar(fontsize = 10),
                 col = col_fun,column_names_rot = 45,  column_names_gp = grid::gpar(fontsize = 10),
                 column_title_gp = gpar(fontsize = 15, fontface = "bold"),
                 row_title_gp = gpar(fontsize = 10, fontface = "bold"))

@@

long_plants_1$Functional_groups[long_plants_1$Functional_groups==1] <- "Short-lived selfers" 
long_plants_1$Functional_groups[long_plants_1$Functional_groups==2] <- "Small outcrossing\nperennials" 
long_plants_1$Functional_groups[long_plants_1$Functional_groups==3] <- "Self-incomp. perennials\nwith large flowers" 
long_plants_1$Functional_groups[long_plants_1$Functional_groups==4] <- "Tall plants with small\nunisexual flowers" 
long_plants_1$Functional_groups[long_plants_1$Functional_groups==5] <- "Short-lived outcrossers with\nlong zygomorphic flowers"

long_plants_1$Functional_groups <- factor(long_plants_1$Functional_groups, levels=c("Short-lived selfers",
"Small outcrossing\nperennials" ,"Self-incomp. perennials\nwith large flowers",
"Tall plants with small\nunisexual flowers" ,"Short-lived outcrossers with\nlong zygomorphic flowers" ))

@@

h_plan <- Heatmap(long_plants_m, name = "Mean\npercentile", row_split=r_split_plants,cluster_row_slices = F, 
                  column_title = "Plant functional groups",row_names_gp = gpar(fontsize = 10),col = col_fun,column_names_rot = 45,  
                  column_names_gp = grid::gpar(fontsize = 10),column_title_gp = gpar(fontsize = 15, fontface = "bold"),
                  row_title_gp = gpar(fontsize = 10, fontface = "bold"))

library(patchwork)
ht_list <- h_pol+h_plan

draw(ht_list, auto_adjust = FALSE, cluster_rows = F)

@@

ggplot(ggd1,offset_labels=-0.05) + theme(panel.grid.major = element_blank(),
 axis.text = element_blank(),axis.title = element_blank()) +
  ggtitle("Plant functional groups")+
  theme(plot.title = element_text(hjust = 0.5, vjust = -2,size = 20,face="bold"))+
  annotate("text", x=140, y=1.65, label= "Self-incomp. perennials with large flowers ", size=2.5)+
  annotate("text", x=380, y=2.15, label= "Tall plants with small unisexual flowers", size=2.5) +
  annotate("text", x=600, y=3.85, label= "Short-lived selfers", size=2.5) +
  annotate("text", x=1400, y=2.05, label= "Short-lived outcrossers with \n long zygomorphic flowers", size=2.5) +annotate("text", x=950, y=2.05, label= "Small outcrossing perennials", size=2.5)
